### 2024-11-07 mycv/subs/papers.tex
Updates in papers
Indicated the corresponding author of JMPS paper
updates in papers

  {B. Jeon, C. N. Tom\'{e}, \underline{Y. Jeong}$^*$}
  {\href{https://dx.doi.org/10.2139/ssrn.4969819)}{A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}}
  {submitted}
  {}

@@

  {Iftekhar A. Riyad, Bjorn Clausen, Daniel J. Savage, \underline{Y. Jeong}, Donald W. Brown, Mark Knezevic}

@@

  {submitted}
  {}

>>>>

  {B. Jeon, \underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.jmrt.2024.11.043}{A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}}
  {Journal of Materials Research and Technology}
  {In press}

@@

  {Iftekhar A. Riyad, Bjorn Clausen, Daniel J. Savage, \underline{Y. Jeong}, Donald W. Brown, Mark Knezevic$^*$}

@@

  {Journal of Mechanics and Physics of Solids}
  {Vol. 194, 105925, 2025}
